Results

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added results till H3

Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female ; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).

@@

To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
We found a highly significant main effect of valence (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), indicating that negative pictures were perceived as more arousing than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalView_con[,7], format = "e")`).
To explore the effect of valence on facial muscle activity(*Corrugator* and *Levator*), we conducted two ANOVA for the active viewing condition.
For *Corrugator* activity, we found a significant main effect of valence (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), indicating that negative pictures evoked greater *Corrugator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrView_con[,7], format = "e")`).
In line with previously reported results, there was a significant main effect of valence for *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures evoked greater *Levator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGLevView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGLevView_con[,7], format = "e")`).

To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).

>>>>

Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female ; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).

@@

#### Subjective arousal and physiological responding
To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
We found a highly significant main effect of valence (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), indicating that negative pictures were perceived as more arousing than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalView_con[,7], format = "e")`).
To explore the effect of valence on facial muscle activity(*Corrugator* and *Levator*), we conducted two ANOVA for the active viewing condition.
For *Corrugator* activity, we found a significant main effect of valence (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), indicating that negative pictures evoked greater *Corrugator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrView_con[,7], format = "e")`).
In line with previously reported results, there was a significant main effect of valence for *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures evoked greater *Levator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGLevView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGLevView_con[,7], format = "e")`).

To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`).
Post-hoc test showed significantly reduced subjective arousal after use of distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[1,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[2,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[3,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[3,7], format = "e")`) compared with active viewing.
However, there were no significant differences between strategies (all $p>.05$).
To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVAS comparing *Corrugator* activity and *Levator* activity of four the strategies.
Regarding *Corrugator* activity, we found a significant main effect of factor strategy (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`).
Post-hoc test revealed reduced *Corrugator* activity during distraction ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[1,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[2,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[3,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrReg_con[3,7], format = "e")`) compared to active viewing.
There were no significant differences between regulation strategies (all $p>.05$).
